### 2017-01-31 Radio/VLA_OH/VLA_3.tex
with some DR's comments

\begin{center}
{\large{\bf{Probing OH Megamaser in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
\end{center}
\vspace{-.8em}
\textbf{OH megamasers and the physical conditions of low- and high-$z$ \galpop}
Studying the properties of high-redshift ($z$) galaxies is crucial to understand the formation and evolution of present-day galaxies.
High-$z$ galaxies are IR-luminous due to their intense bursts
of obscured star formation and/or their central active galactic nuclei (AGNs),
which are sustained by their massive molecular gas reservoirs ($M_{\rm gas}$$>$10$^{10}$\,\Msun; see \citealt{CW13} for a review).
% Their high IR luminosity imply that they are responsible for building most of the stellar mass in the universe.
The gas-rich and starbursting nature of high-$z$ galaxies may be a result of galaxy mergers
\citep{Riechers11a, Hayward12a, Riechers13b}, or cold gas accretion from the cosmic web \citep[e.g.,][]{Dekel09b}.
% , consistent with the notion that galaxies grow through hierarchical merging \citep{White91a}.
Since the merger rate is expected to increase towards higher redshift \citep[e.g.,][]{LeFloch05a, Magnelli09a}, constraining
its evolution allows us to track the origin and evolution of present-day populations. % emergence of current day populations.

%Galaxies with high IR-luminous and intense star formation are important for the build-up of stellar mass in the universe. 
%While IR-luminous galaxies are found in both nearby and at high $z$, studies find that they display different properties and 
%are different galaxy populations. Low-$z$ ULIRGs are predominantly more compact,
%mostly merger-triggered starbursts, with lower molecular 
%gas mass fractions \citep{Veilleux02a, Hopkins10a, Rujopakarn11a, Rujopakarn13a}, whereas 
%\highz galaxies are a combination of mergers and cold gas accretion.

\noindent The steep dependence between OH and FIR luminosities ($L_{\rm OH}\propto L_{\rm FIR}^2$; \Fig{model}a)
found in local OH ``megamasers'' (OHMs;  see \citealt[]{Lo05a} for a review) and
the ubiquity of strong IR-emitting galaxies found at high $z$ suggest that
the number density of OHM may improve current constraints on
the cosmic merger history \citep[hereafter DG02]{Darling02b_LF}. % but that's assuming IR-luminous must be driven by mergers....
Existing models predict that detections of
OHMs out to at least $z$\ssim3 are possible with current facilities (e.g. the GBT; \Fig{model}b).
Yet, despite several attempts,
the most distant OHM known-to-date was discovered over two decades ago, at $z$\eq0.265 \citep{Baan92a}.
The null detection in a $z$\ssim4 extremely IR-bright galaxy (\LIR$>10^{14}$\Lsun; \citealt{Ivison06a}) and
the remarkably low detection rate (7\%) from a sample of $>$120 IR-luminous galaxies
at $z$\,$\lesssim$\,1.5 ($L_{\rm IR}>10^{11}$\Lsun; \Fig{model}b; \citealt{Willett12a})
suggest a potential redshift evolution in the \LOH-\LFIR relation.
Detecting OHM beyond $z$\eq0.265 is therefore needed to enable a better understanding of the
OHM trigger mechanism, which may differ at earlier epochs due to different physical conditions of galaxies,
and to improve existing predictions to plan for future OHM surveys with upcoming facilities
\citep[e.g., FAST, APERTIF/WSRT, ASKAP;][]{Zhang14b}.
Here we propose to observe OH 1667 MHz line emission in the
gravitationally-lensed starbursting galaxy merger
RXJ1131 at $z$\eq0.65 (\Fig{hst}) using the VLA's B-array configuration.

\noindent \textbf{An ideal target --- a lensed gas-rich, starbursting merger at $z$\,$>$\,0.6}\\
\noindent High-resolution imaging and spectroscopy in optical wavelength show that RXJ1131 is
lensed by a foreground galaxy at $z$\ssim0.3 (\Fig{hst}; \citealt{Sluse03a}).
The unique lensing configuration of RXJ1131 has led to extensive follow-up studies spanning X-ray to radio \citep[\Fig{hst}e; e.g.,][]{Claeskens06a, Sluse07a, Leung17a},
making it one of the best-studied galaxies at $z$$>$0.5 and
the only source at 0.2$<$$z$$<$1 with spatially-resolved imaging of the molecular gas distribution \citep{Leung17a}.
% X-ray studies  a highly compact source of emission
% in the innermost region near the accretion disk down to pc-scale
% \citep[$\sim$20\,AU][]{Dai10a}.
Modeling of the X-ray spectrum reveals substantial amount of neutral gas with column density of
 % The continuum is strongly absorbed at soft energies by a
$N_{\rm H}\sim$10$^{23}$ cm$^{-2}$ in the innermost region near % the accretion disk % w.in the X-ray emitting region
% The spectrum at lower energies is heavily absorbed by neutral gas with a hydrogen column density $N_{\rm H}$.
% Soft X-ray continuum suggest the presence of a substantial amount of gas.
the $L_X$$\gtrsim$10$^{45}$\,\Lsun AGN \citep{Pooley07a, Reis14a}.
Our best-fit spectral energy distribution (SED) model indicates
a strong apparent far-IR luminosity of \LFIR$\sim$5\E{12}\Lsun, which corresponds to
an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
The large column density together with the strong FIR radiation field % of $\sim$10$^{12}$\Lsun (lensing-corrected),
% recent star formation (as traced by rest-frame UV emission),
% presence of a nearby companion, and % at $\sim$2.4\,kpc away, and
and the large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun (\Fig{hst}b, c)
are favourable for generating OH masers, making RXJ1131 an ideal candidate
to search for OHMs beyond the nearby universe.

\noindent In addition, the redshift of RXJ1131 has been spectroscopically confirmed with CO lines down to a precision of
$\Delta z$\eq0.0002, indicating that the proposed OH line is redshifted to a fortuitous region
free of RFI at the low-end of the L-band.
Together with the high fringe rate of the B-array configuration, the proposed \obs will
reach a sensitivity deeper than previous high-$z$ OHM searches beyond $z$$>$0.4, which were carried out
with single-dish telescopes \citep[\Fig{model}b; e.g.][]{Darling02a, Willett12a}.
Assuming the Malmquist-bias corrected relation
($L_{\rm OH}\propto L_{\rm FIR}^{1.2}$; DG02), we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun (orange marker in \Fig{model}b). 
We here aim to detect the OHM in RXJ1131 at 5$\sigma$. 
By exploiting the effect of lensing magnification, we require an {\bf on-source time of 4.3 hours}, which
is {\bf $\sim$30 times cheaper}
 % sigma scales as 1/root(t) --> t scales as 1/sigma^2
than otherwise possible.

\noindent \underline{\textbf{Science goals}}
\vspace{.2em}\\
$\bullet$ {\bf Testing OHM as a tracer of merger.}
The proposed \obs will establish the first OHM measurement in a {\it bona-fide} high-$z$ merger, thereby
demonstrating the feasibility of using it as a tracer of distant mergers and
testing the long-envisaged hypothesis of using its number density to constrain
the redshift evolution of merger rate.
Such a detection will also allow us to better constrain the
\LOH-\LFIR relation out to higher $z$, % which may provide a handle on the pumping efficiency (\LOH/\LFIR)
% that may be closer to other high-$z$ galaxies if their physical conditions are more similar than compared to low-z (\LOH/\LFIR)
and thus improve predictions on the required sensitivity needed for future searches of high-$z$ OHMs.
Since our target is a merger,
a null detection would also indicate that the notion of
using the OHM number density to constrain the merger history requires revision before designing future OHM surveys.

%
% OHM help us understand the physical conditions of high-z galaxies: different circumnuclear environment, optical depth? - likely already know about the cirucmnuclear env part from X-ray, but then could be use for other high-z sources w/o detailed characterization?
\noindent $\bullet$ {\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies.}
% Classical model: foreground amplification of background radio continuum, expect quadratic relationship, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud.
Null detections in previous high-$z$ OHM searches suggest a shallower \LOH-\LFIR dependence, which may be
reflecting the different physical conditions of the inner few hundred pc (where OHMs are generated)
between low- and high-$z$ IR-luminous galaxies.
The lower \LOH/\LFIR indicate that the OH amplification is less efficient at the same FIR luminosity
and that collisional pumping (e.g. due to the strong AGN, and high gas mass and density; \citealt{Field94a}) % volume density
% while locally, not all OHM are AGN hosts, suggesting the FIR radiation from the SB is the dominant pumping source, but the non-detection based on local extrapolation and such maser model may suggest a different energy source/powering mechanism at higher-z, where quasars are more active, and may indicate that something about AGN/radio pumping
%
% Since a purely radiative pumping mechanism is possible
% only at relatively low densities ($n_{\rm OH}$\ssim10$^{-4}$\,cm$^{-3}$), and collisional processes can theoretically predominate at high OH densities, and saturated amplification can become important \citep{Field94a}.
may play a dominant role in these gas-rich \highz systems.
Obtaining a definitive OHM measurement in RXJ1131 will provide a handle on the OH pumping efficiency (\LOH/\LFIR) out to higher $z$.
This together with the detailed properties derived for our target (e.g., \LFIR, \LIR, SFR, $L_{\rm radio}$, molecular and dust content)
will elucidate the role of collisional over radiative pumping
that may be prevalent in \highz galaxies given their physical properties, which are more similar to RXJ1131 than
local starbursts. % more violent star formation in a more gas-rich turbulent ISM.
	% [NOT applicable] Since the optical depth increases with FIR radiation field, the simple picture of low-gain amplification
	% (i.e., unsaturated masing) found to be consistent with local OHMs...
	%
% % implying the simple picture of low-gain amplification (i.e., unsaturated masing, quadrature, low density)  \citep{Henkel90a,Randell95a} found to be consistent with local OHMs will likely break down; (i.e., not all OHMs are unsaturated).
% While in the nearby universe (z\ssim0), OHMs appear to be unsaturated.

\noindent $\bullet$ {\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies.}
The much broader linewidths found in $z$$>$0.2 OHMs compared to those at $z$\eq0 already indicate
different dynamical properties in the innermost regions of their hosts \citep{Baan92a,Darling02a}.
Detecting the OHM in RXJ1131 will therefore demonstrate the feasibility of
using it as a trace of the kinematics in the circumnuclear regions of \highz galaxies, which will improve
our understanding of the internal dynamics of IR-luminous, starbursting galaxies at high $z$.

\noindent $\bullet$ {\bf Radio continuum.}
In addition, the proposed \obs will provide an additional constraint on the radio continuum emission at 1\,GHz
towards RXJ1131 (\Fig{hst}e).

% --- finally ----
\noindent
With the aid of lensing and the rich multi-wavelength data available for this potential OHM host, RXJ1131 is an exceptional target
for high-$z$ OHM search.
Detecting the OHM will provide a handle on the pumping efficiency (\LOH/\LFIR)
and enable a better understanding of the OHM triggering mechanism at $z$\ssim0.65, which
would reflect the different physical conditions between low- and high-$z$ IR-luminous galaxies.
The detection will also demonstrate the utility of OHMs as tracers of distant mergers, and
of the kinematics in the inner few hundred pc
of starburst galaxies beyond the nearby universe. %, out to a lookback time of $\sim$6 Gyr.
The proposed investigation will therefore serve as an
important benchmark for future studies of high-$z$ OHMs out to earlier epochs,
when extremely IR-luminous sources are much more common.

@@

\begin{figure}[ptbh]
\includegraphics[trim=10 305 270 0, clip, scale=0.825]{Fig/OHFIR} \hspace{-1.25em}
% \includegraphics[trim=0 400 200 0, clip, scale=0.85]{Fig/Darling02b_distribution}
%  \includegraphics[trim=0 0 0 0, clip, scale=0.625]{Fig/Willett11_distribution}\\ \vspace{1.5em}
% \includegraphics[trim=0 0 0 0, clip, scale=0.42]{Fig/Darling02_predictionf4}
\includegraphics[trim=0 -20 155 0, clip, scale=0.41]{Fig/willett12_fig1_mod.pdf}
\caption{{\bf \LOH-\LFIR correlation and existing OHMs measurements}
{\it (a):} Since the OH line strength increases with \LFIR,
the ubiquity of IR-luminous galaxies at high $z$ suggest that OHM can be used to trace distant mergers
($L_{\rm IR}$$\gtrsim$10$^{12}$\Lsun; DG02).
{\it (b):} The highest-$z$ OHM known ($z$\eq0.265) was discovered over two decades ago.
A remarkably low detection rate of $\sim$7\% was reported in subsequent surveys (black and green symbols),
suggesting a potential redshift evolution in the \LOH/\LFIR relation
due to the different physical properties between low- and high-$z$ IR-luminous galaxies.
Assuming $L_{\rm OH}\propto L_{\rm FIR}^{1.2}$ (Malmquist-bias corrected; DG02),
we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun in our target (orange marker). (Figure adopted from
\citealt{Willett12a})
Here we propose to observe OH 1667 MHz line emission in the gravitationally-lensed starbursting
galaxy merger RXJ1131 at $z$\eq0.65.
The proposed sensitivity will
probe deeper than existing OHM surveys, and to fainter intrinsic (i.e., lensing-corrected) \LOH beyond $z$$\gtrsim$0.2.
Detecting the OHM in RXJ1131 will provide the first measurement beyond $z$$>$0.265,
which will improve predictions on the sensitivity needed for future high-$z$ OHM surveys with upcoming facilities.
\label{fig:model}}
\end{figure}

\begin{figure}[ptbh]
% \hspace{-1.6em}
\centering
\includegraphics[trim=0 0 300 0, clip, scale=.75]{Fig/Fig2}
\vspace{-0.25em}
\caption{
{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\,$>$\,0.6 with a well-sampled spectral energy distribution (SED) spanning rest-frame UV to radio.}
{\em (a):} Source-plane reconstruction of {\it HST} images shows recent star formation in our target and
the presence of a nearby companion (\citealt{Claeskens06a}).
{\em (b):}
The UV starlight in RXJ1131 is lensed into an Einstein ring (diameter $\sim$3.6") and the central AGN is
quadruply-lensed in the {\it HST} image (grayscale). Both star formation and AGN are sustained
by the extended CO gas reservoir \citep[contours; ][]{Leung17a}.
{\em (c):}
Our CO \obs reveal a massive molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 and
confirmed the presence of the nearby companion, with a gas mass ratio of 7:1 \citep{Leung17a}.
{\em (d):}
We have detected strong radio continuum at 5\,GHz towards this target.
The proposed \obs will provide an additional constraint at 1\,GHz (orange marker in \Fig{hst}e).
{\em (e):} Our best-fit SED model indicates a strong apparent far-IR radiation of \LFIR$>$4\E{12}\,\Lsun, corresponding to
an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
The massive gas reservoir, on-going star formation with high \LFIR, and the large gas column density
are favourable for generating OHM, making RXJ1131 an
ideal candidate to search for OHM beyond the nearby universe.
Here we aim to detect the OHM in RXJ1131, and thus obtain a handle on the pumping efficiency
to better understand the triggering mechanism at a look-back time of 6 Gyr, which
would reflect the different physical conditions of the innermost regions between low- and high-$z$ IR-luminous galaxies.
The proposed \obs is thus an important step towards understanding the evolution of the inner few hundred pc of
IR-luminous galaxies.
\label{fig:hst}}
\end{figure}

>>>>

\begin{center}
{\large{\bf{OH Megamaser Emission in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
\end{center}
\vspace{-.8em}
\textbf{OH megamasers and the physical conditions of low- and high-$z$ \galpop}
Galaxies with high IR-luminousity and thus intense star formation rates are important for the build-up of stellar mass in the universe. 
While IR-luminous galaxies ($\gtrsim10^{12}$\Lsun; ULIRGs) 
exist at both low and high redshift ($z$), recent studies indicate that they are not the same population. 
Low-$z$ ULIRGs are mostly merger-triggered starbursts which are more compact and contain
less molecular gas compared to their \highz counterparts \citep{Veilleux02a, Hopkins10a, Rujopakarn11a, Rujopakarn13a},
where \highz starbursts are driven by cold gas accretion \citep[e.g.,][]{Dekel09b} 
and/or galaxy mergers \citep{Riechers11a, Riechers13b, Hayward12a}.
Probing the kinematics, dynamical structures, and physical conditions of the inner regions of \highz ULIRGs 
and comparing them to those observed at low $z$ 
are necessary to enable a better understanding of starbursting galaxies at different epochs.
% a comparison with their local analogs are important to enable a better understanding of the nature of these \galpop and
% to shed light on their formation and evolution processes.
% improve our understanding of the formation and evolution of low- and \highz starburts.
However, measuring these properties at high $z$ (e.g., $\sim$8\,kpc/$''$ at $z$=1)
% measuring the kinematics in the inner regions of high-$z$ galaxies 
require sub-arcsec resolution or better with typical line tracers. On the other hand, a 
steep relation ($L_{\rm OH}\propto L_{\rm FIR}^{1.2-2}$; \Fig{model}a) has been found in nearby OH ``megamasers'' 
(OHMs), which are generated in the inner few hundred pc of U/LIRGs (see \citealt[]{Lo05a} for a review).
Given the ubiquity of IR-bright galaxies at high-$z$, we propose that OHM may be used as a tracer to 
study the kinematics of the inner regions of \highz galaxies.
In fact, the much broader linewidths found in $z$$>$0.2 OHMs compared to those at $z$=0 already hint at the feasibility of 
this diagnostic \citep[hereafter DG02]{Baan92a, Darling02a}.

\noindent Existing models predict that detections of
OHMs out to at least $z$\ssim3 are possible with current facilities (e.g. the GBT; \Fig{model}b; \citealt{Darling02b_LF}).
Yet, despite several attempts,
the most distant OHM known-to-date was discovered over two decades ago, at $z$\eq0.265 \citep{Baan92a}.
The null detection in a $z$\ssim4 extremely IR-bright galaxy (\LIR$>10^{14}$\Lsun; \citealt{Ivison06a}) and
the remarkably low detection rate (7\%) from a sample of $>$120 IR-luminous galaxies
at $z$\,$\lesssim$\,1.5 ($L_{\rm IR}>10^{11}$\Lsun; \Fig{model}b; \citealt{Willett12a})
suggest a potential redshift evolution in the \LOH-\LFIR relation.
Detecting OHM beyond $z$\eq0.265 is therefore needed to enable a better understanding of the
OHM trigger mechanism, which may differ at earlier epochs due to different physical conditions of galaxies,
to demonstrate the utility of using it a tracer of the kinematics in the inner regions of high-$z$ galaxies (with upcoming facilities,
e.g., FAST, APERTIF/WSRT, ASKAP; \citealt[][]{Zhang14b}),
and to improve existing predictions for future OHM surveys with these facilities.
Here we propose to observe OH 1667 MHz line emission in the
gravitationally-lensed starbursting galaxy merger
RXJ1131 at $z$\eq0.65 (\Fig{hst}) using the VLA's B-array configuration.

\noindent \textbf{An ideal target --- a lensed gas-rich, starbursting merger at $z$\,$>$\,0.6}\\
\noindent High-resolution imaging and spectroscopy in optical wavelength show that RXJ1131 is
lensed by a foreground galaxy at $z$\ssim0.3 (\Fig{hst}; \citealt{Sluse03a}).
The unique lensing configuration of RXJ1131 has led to extensive follow-up studies spanning X-ray to radio \citep[\Fig{hst}e; e.g.,][]{Claeskens06a, Sluse07a, Leung17a},
making it one of the best-studied galaxies at $z$$>$0.5 and
the only source at 0.2$<$$z$$<$1 with spatially-resolved imaging of the molecular gas distribution \citep{Leung17a}.
Modeling of the X-ray spectrum reveals substantial amount of neutral gas with column density of
$N_{\rm H}\sim$10$^{23}$ cm$^{-2}$ in the innermost region near 
the $L_X$$\gtrsim$10$^{45}$\,\Lsun AGN \citep{Pooley07a, Reis14a}.
Our best-fit spectral energy distribution (SED) model indicates
a strong apparent far-IR luminosity of \LFIR$\sim$5\E{12}\Lsun, which corresponds to
an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected), and a cold dust temperature of $T_{d}$\eq55K
(i.e., based on FIR/submm photometry).
The large column density together with the strong FIR radiation field % of $\sim$10$^{12}$\Lsun (lensing-corrected),
% recent star formation (as traced by rest-frame UV emission),
and the large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun (\Fig{hst}b, c)
are favourable for generating OH masers, making RXJ1131 an ideal candidate
to search for OHMs beyond the nearby universe.

\noindent In addition, the redshift of RXJ1131 has been spectroscopically confirmed with CO lines down to a precision of
$\Delta z$\eq0.0002, indicating that the proposed OH line is redshifted to a fortuitous region
free of RFI at the low-end of the L-band.
Together with the high fringe rate of the B-array configuration, the proposed \obs will
reach a sensitivity deeper than previous high-$z$ OHM searches beyond $z$$>$0.4, which were carried out
with single-dish telescopes \citep[\Fig{model}b; e.g.][]{Darling02a, Willett12a}.
Assuming the Malmquist-bias corrected relation
($L_{\rm OH}\propto L_{\rm FIR}^{1.2}$; DG02), 
we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun (orange marker in \Fig{model}).
Since Mrk 231 --- the only OHM host with an AGN and starburst, and thus the most similar to RXJ1131 ---
falls above this relation, our assumption and estimation of the required sensitivity are reasonable.
We here aim at a 7$\sigma$ detection.
By exploiting the effect of lensing magnification, we require an {\bf on-source time of 8 hours}, which
is {\bf $\gtrsim$30 times cheaper}
 % sigma scales as 1/root(t) --> t scales as 1/sigma^2
than otherwise possible.

\noindent \underline{\textbf{Science goals}}
\vspace{.2em}\\
\noindent $\bullet$ {\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies.}
Null detections in previous high-$z$ OHM searches suggest a shallower \LOH-\LFIR dependence, which may be
reflecting the different physical conditions of the inner few hundred pc (where OHMs are generated)
between low- and high-$z$ IR-luminous galaxies.
The lower \LOH/\LFIR indicate that the OH amplification is less efficient at the same FIR luminosity
and that collisional pumping (e.g. due to the strong AGN, and high gas mass and density; \citealt{Field94a}) % volume density
%
% Since a purely radiative pumping mechanism is possible
% only at relatively low densities ($n_{\rm OH}$\ssim10$^{-4}$\,cm$^{-3}$), and collisional processes can theoretically predominate at high OH densities, and saturated amplification can become important \citep{Field94a}.
may play a dominant role in these \highz gas-rich systems.
Obtaining a definitive OHM measurement in RXJ1131 will provide a handle on the OH pumping efficiency (\LOH/\LFIR) out to higher $z$.
This together with the detailed properties derived for our target (e.g., \LFIR, \LIR, SFR, $L_{\rm radio}$, $T_{d}$, molecular and dust content)
will elucidate the role of collisional over radiative pumping
that may be prevalent in \highz galaxies, given that their physical properties are more similar to RXJ1131 than
local starbursts. % more violent star formation in a more gas-rich turbulent ISM.
%	% [NOT applicable] Since the optical depth increases with FIR radiation field, the simple picture of low-gain amplification
%	% (i.e., unsaturated masing) found to be consistent with local OHMs...
%	%
%% % implying the simple picture of low-gain amplification (i.e., unsaturated masing, quadrature, low density)  \citep{Henkel90a,Randell95a} found to be consistent with local OHMs will likely break down; (i.e., not all OHMs are unsaturated).
%% While in the nearby universe (z\ssim0), OHMs appear to be unsaturated.

\noindent $\bullet$ {\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies.}
The much broader linewidths found in $z$$>$0.2 OHMs \citep[typically at least a factor of $>$2 in FWHM;][DG02]{Baan92a}
compared to those at $z$\eq0 already indicate
different dynamical properties in the innermost regions of low- and high-$z$ OHM hosts.
Detecting the OHM in RXJ1131 will therefore demonstrate the feasibility of
using it as a tracer of the kinematics in the circumnuclear regions of \highz galaxies, thereby improving
our understanding of the internal dynamics of IR-luminous, gas-rich, starbursting galaxies at high $z$.

\noindent $\bullet$ {\bf Testing OHM as a tracer of mergers.}
The proposed \obs will establish the first OHM measurement in a {\it bona-fide} high-$z$ merger, thereby
demonstrating the feasibility of using it as a tracer of distant mergers and
testing the long-envisaged hypothesis of using its number density to constrain
the redshift evolution of merger rate (DG02).
Such a detection will also allow us to better constrain the
\LOH-\LFIR relation out to higher $z$, % which may provide a handle on the pumping efficiency (\LOH/\LFIR)
% that may be closer to other high-$z$ galaxies if their physical conditions are more similar than compared to low-z (\LOH/\LFIR)
and thus improve predictions on the required sensitivity needed for future searches of high-$z$ OHMs.
Since our target is a merger,
a null detection would also indicate that the notion of
using the OHM number density to constrain the merger history requires revision before designing future OHM surveys.

\noindent $\bullet$ {\bf Radio continuum.}
The proposed \obs will also constrain the 1\,GHz radio continuum emission
towards RXJ1131 (\Fig{hst}e), providing a useful estimate for future observations with the A-array configuration to
constrain the spectral index and synchrotron emission in the foreground radio galaxy 
and in the background quasar (our target RXJ1131; \Fig{hst}d, e).

% --- finally ----
\noindent
With the aid of lensing and the rich multi-wavelength data available for this potential OHM host, RXJ1131 is an exceptional target
for high-$z$ OHM search. 
Detecting the OHM will provide a handle on the pumping efficiency (\LOH/\LFIR)
and enable a better understanding of the OHM triggering mechanism at $z$\ssim0.65, which
would reflect the different physical conditions between low- and high-$z$ IR-luminous galaxies.
The detection will also demonstrate the utility of OHMs as tracers of distant mergers, and
of the kinematics in the inner few hundred pc
of starburst galaxies beyond the nearby universe. %, out to a lookback time of $\sim$6 Gyr.
The proposed investigation will therefore serve as an
important benchmark for future studies of high-$z$ OHMs out to earlier epochs,
when extremely IR-luminous starbursting sources are much more common.

@@

\begin{figure}[ptbh]
\includegraphics[trim=0 0 0 0, clip, scale=0.82]{Fig/OHFIR_RXJ} % \hspace{-1.25em}
\includegraphics[trim=0 -20 155 0, clip, scale=0.41]{Fig/willett12_fig1_mod.pdf}
\caption{{\bf \LOH-\LFIR correlation and existing OHMs measurements}
{\it (a):} Since the OH line strength increases with \LFIR,
the ubiquity of IR-luminous galaxies at high $z$ suggest that OHM may be a used as a proxy for
studying the kinematics of the inner regions of distant galaxies.
(Figure modified from DG02).
{\it (b):} The highest-$z$ OHM known ($z$\eq0.265) was discovered over two decades ago.
Subsequent surveys (black and green symbols) suggest a potential redshift evolution in the \LOH/\LFIR relation
due to the different physical properties between low- and high-$z$ IR-luminous galaxies, but 
severe RFI contaminations at $\nu_{\rm obs}$$<$1\,GHz inhibit a definitive conclusion. (Figure adopted from
\citealt{Willett12a}).
Here we propose to observe OH 1667 MHz line emission in the gravitationally-lensed starbursting
galaxy merger RXJ1131 at $z$\eq0.65.
Assuming $L_{\rm OH}\propto L_{\rm FIR}^{1.2}$ (Malmquist-bias corrected; DG02),
we expect an apparent \LOH= 3.3\E{3}\,\Lsun in our target (orange marker). The proposed sensitivity will
probe deeper than existing OHM surveys (we do not expect RFI contamination at the 
redshifted line frequency), 
and to fainter intrinsic (i.e., lensing-corrected) \LOH beyond $z$$\gtrsim$0.2.
Detecting the OHM in RXJ1131 will provide the first measurement beyond $z$$>$0.265,
which will improve predictions on the sensitivity needed for future high-$z$ OHM surveys with upcoming facilities.
\label{fig:model}}
\end{figure}

\begin{figure}[ptbh]
% \hspace{-1.6em}
\centering
\includegraphics[trim=0 190 0 0, clip, scale=.77]{Fig/Fig2}
\vspace{-0.85em}
\caption{
{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\,$>$\,0.6}
{\em (a):} Source-plane reconstruction of {\it HST} images shows recent star formation in our target and
the presence of a nearby companion (\citealt{Claeskens06a}).
{\em (b):}
The UV starlight in RXJ1131 is lensed into an Einstein ring (diameter $\sim$3.6") and the central AGN is
quadruply-lensed in the {\it HST} image (grayscale). Both star formation and the AGN are sustained
by the extended CO gas reservoir \citep[contours; ][]{Leung17a}.
{\em (c):}
Lens modeling of our CO data (yellow) 
reveals a massive gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 
(cyan; magnification factors $\mu_{L}$ are annotated above the respective channels) and
confirmed the presence of a CO-emitting companion, with a gas mass ratio of 7:1 \citep[bottom panel;][]{Leung17a}.
{\em (d):}
We have detected strong radio continuum at 5\,GHz towards this target.
The proposed \obs will provide an additional constraint at 1\,GHz (orange marker in \Fig{hst}e).
{\em (e):} Our best-fit SED model indicates a strong apparent far-IR radiation of \LFIR$>$4\E{12}\,\Lsun, corresponding to
an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
The massive gas reservoir, on-going star formation with high \LFIR, and the large gas column density
are favourable for generating OHM, making RXJ1131 an
ideal candidate to search for OHM beyond the nearby universe.
Here we aim to detect the OHM in RXJ1131, and thus to obtain a handle on the pumping efficiency
to better understand the triggering mechanism at a look-back time of 6 Gyr, which
would reflect the different physical conditions of the innermost regions between low- and high-$z$ IR-luminous galaxies.
The proposed study is therefore an important step towards understanding 
% the evolution of the inner few hundred pc of
the internal structure and kinematics of
starbursting galaxies at earlier epochs.
\label{fig:hst}}
\end{figure}
